Experiments with Synthetic Data

### 2022-07-13 dev/notebooks/synthetic.qmd
finally sorted out stuff on CounterfactualExplanations side and basic experiment code now running.

```{julia}
i = 2
while i <= 10
    counterfactual_data′ = CounterfactualData(X′,y′')
    Random.seed!(123)
    candidates = findall(y′.==0)
    chosen = rand(candidates, Int(round(μ*length(candidates))))
    mod = Models.train(mod, counterfactual_data′; n_epochs=n_epochs)
    for i in chosen
        x = X′[:,i]
        outcome = generate_counterfactual(x, 1, counterfactual_data, mod, gen; γ=γ)
        X′[:,i] = counterfactual(outcome)
        y′[i] = counterfactual_label(outcome)
    end
    i += 1
end
plt_single_repeat = plot(mod,counterfactual_data′;zoom=0,colorbar=false,title="(d)")
```

@@

@@

```{julia}
# Variables:
μ = [0.05,0.1,0.25]
γ = [0.50,0.75,0.9]
grid_ = Experiments.GridVariables(μ, γ)
n_rounds = 10
n_folds = 5
target = 1.0
T = 1000
```

>>>>

```{julia}
i = 2
while i <= 10
    counterfactual_data′ = CounterfactualData(X′,y′')
    Random.seed!(123)
    candidates = findall(y′.==0)
    chosen = rand(candidates, Int(round(μ*length(candidates))))
    H₀ = mod.model.H # use posterior as new prior
    mod = Models.train(mod, counterfactual_data′; n_epochs=n_epochs, H₀=H₀)
    for i in chosen
        x = X′[:,i]
        outcome = generate_counterfactual(x, 1, counterfactual_data, mod, gen; γ=γ)
        X′[:,i] = counterfactual(outcome)
        y′[i] = counterfactual_label(outcome)
    end
    i += 1
end
plt_single_repeat = plot(mod,counterfactual_data′;zoom=0,colorbar=false,title="(d)")
```

@@

![](../artifacts/upload/www/synthetic/poc.png)

@@

```{julia}
using AlgorithmicRecourseDynamics.Experiments
# Variables:
μ = [0.05,0.1,0.25]
γ = [0.50,0.75,0.9]
grid_ = Experiments.GridVariables(μ, γ)
n_rounds = 5
n_folds = 1
target = 1.0
T = 1000
```
